%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Compiler Engineer} % Job title
    {Advanced Micro Devices, Inc.} % Organization
    {Austin, Texas} % Location
    {May. 2022 - current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Studied the factors affecting verification errors for convolution end-to-end tests with fp16 data type.}
      \item {Improved CI infrastructure for multi-arch testing.}
      \item {Developed an automation framework to generate convolution end-to-end tests.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Compiler Engineer Intern} % Job title
    {Mathworks} % Organization
    {Natick, MA} % Location
    {Jun. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Developed a C++ pass to analyze for loops in the IR to find loop invariant
        variables.
      \item Generated intrinsic functions which expand to OpenMP pragmas in the code
        generation phase.
      \item Performed timing experiments of the generated code on multi-core systems.
      \end{cvitems}
    }

% ---------------------------------------------------------
  \cventry
    {Graduate Research Assistant}
    {The University of Texas at Austin}
    {Austin, Texas}
    {Jun. 2013 - Dec. 2021}
    {
      \begin{cvitems}
      \item {Implemented Monte Carlo Localization on heterogeneous systems}
      \item {Implemented particle filter on heterogeneous systems}
      \item {Developed an analytical performance model for GPGPU kernels} % title
      \item {Develop a laser power control system for Selective Laser Sintering} % title
      \end{cvitems}
    }
% ---------------------------------------------------------
\end{cventries}
