%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% ---------------------------------------------------------
  \cvresearchentry
  {Implementation of Monte Carlo Localization on Heterogeneous Systems} % title
  {May. 2021 - Aug. 2021} % date
  {% description
    \begin{cvitems}
    \item Implemented the Monte Carlo Localization algorithm in CUDA.
    \item Partitioned the particles among multiple threads: one launches the
      GPU kernel and others run on CPU in a multi-threaded manner.
    \item Mutex and condition variables were used to synchronize between threads.
    \item Simulated the localization of the f1tenth autonomous car system using ROS.
    \end{cvitems}
  }

% ---------------------------------------------------------
  \cvresearchentry
  {Implementation of Particle Filter on Heterogeneous Systems} % title
  {Jan. 2021 - Apr. 2021} % date
  {% description
    \begin{cvitems}
    \item Partitioned the particles among two processes: one runs on CPU and the
      other launches the GPU kernel.
    \item POSIX shared memory and System V semaphore were used to communicate and
      synchronize between the two processes.
    \item Conducted experiments on NVIDIA GTX TITAN and Jetson TX2 to obtain the
      optimal partition among CPU and GPU.
    \end{cvitems}
  }

% ---------------------------------------------------------
  \cvresearchentry
  {An Analytical Performance Model for GPGPU kernels} % title
  {Jan. 2019 - Dec. 2020} % date
  {% description
    \begin{cvitems}
    \item Developed a mathematical model to estimate the execution time of simple
      kernels based on static analysis of CUDA assembly code and knowledge of GPU
      architecture.
    \end{cvitems}
  }

% ---------------------------------------------------------
  \cvresearchentry
  {Laser Power Control for Selective Laser Sintering} % title
  {Sep. 2016 - Aug. 2017} % date
  {% description
    \begin{cvitems}
    \item Achieved motion detection of galvanometer
      by comparing two consecutive images taken by infrared cameras in LabVIEW.
    \item Built an automatic laser power control system at both vector-level
      and layer-level control granularity to eliminate thermal
      gradients in the post-sintering temperature on the Laser Additive
      Manufacturing Pilot System at the department of mechanical engineering.
    \end{cvitems}
  }

% ---------------------------------------------------------
  \cvresearchentry
  {A MATLAB to CUDA translator for Particle Filter Applications} % title
  {Sep. 2014 - Aug. 2015} % date
  {% description
    \begin{cvitems}
    \item Developed a front-end in C to translate MATLAB code of particle filter
      estimator into CUDA code.
    \item Developed domain-specific optimization passes in C for the generated
      CUDA code.
    \end{cvitems}
  }

% ---------------------------------------------------------
  \cvresearchentry
  {CUDA Implementation of Particle Filter for Real World Applications} % title
  {Jun. 2013 - Aug. 2014} % date
  {% description
    \begin{cvitems}
    \item Applications include Vacuum Arc Remelting and Early Kick Detection.
    \item Implemented sampling, importance, and resampling modules in CUDA.
    \item Analyzed and improved GPU kernel performance through profiling.
    \end{cvitems}
  }

  
%---------------------------------------------------------
\end{cventries}